### 2016-01-28 paper.tex
Image for SA-ADC
R-2R DAC correction
Mixed circuit PUF changes

%Disadvantage of intrinsic puf and why our model is better.
\section{ADC and DAC}
A Digital to Analog Converter(DAC) as the name suggests converts digital data to an analog quantity like voltage. A n-bit DAC can be constructed easily using a R-2R ladder which consists of n R-2R networks. Each network is fed with a reference voltage(say $V_{ref}$) for a set bit or zero voltage for a 0 bit. A R-2R network in the ladder causes the voltage to be split accordingly to its bit position. For a n-bit DAC, output voltage varies from 0 to $(1-\frac{1}{2^{n}})*V_{ref}$ in steps of $\frac{1}{2^{n}}*V_{ref}$. A R-2R DAC suffers from thermal noise which increases with resistance and temperature. The PUF output variation can occur because of microscopic variations in the resistors and switches used.

@@

\section{Mixed Circuit based PUF}

>>>>

%Disadvantage of intrinsic puf and why our model is better.
\section{ADC and DAC}
A Digital to Analog Converter(DAC) as the name suggests converts digital data to an analog quantity like voltage. A n-bit DAC can be constructed easily using a R-2R ladder which consists of n R-2R networks. Each network is fed with a reference voltage(say $V_{ref}$) for a set bit or zero voltage for a 0 bit. A R-2R network in the ladder causes the voltage to be split accordingly to its bit position. For a n-bit DAC, output voltage varies from 0 to $(1-\frac{1}{2^{n}})*V_{ref}$ in steps of $\frac{1}{2^{n}}*V_{ref}$. A R-2R DAC suffers from thermal noise which increases with resistance and temperature. The PUF output variation can occur because of microscopic variations in the resistors and switches used.
\begin{figure}[H]
\includegraphics[scale=0.8]{SA-ADC.png}
\centering
\caption{Block diagram of a 4-bit R-2R DAC}
\end{figure}

@@

\section{Mixed Circuit based PUF}
In any electronic device, we encounter conversions from analog form to digital form and vice versa. Consider
two people speaking through a mobile phone. Sound is converted to an analog signal by the microphone, which is
then converted to digital form by an analog to digital converter(ADC) for transmission. In the other end, the digital
data is converted to analog by a digital to analog converter(DAC) and the speaker converts to audible sound. In this
digitalizing world, ADC and DAC modules are omnipresent in all devices. The main reason behind this is that all the input from
the external world is analog in nature and the device process everything digitally. This factor plays a key role in
the idea of using ADC and DAC components for PUFs. The ADC and DAC modules can be embedded inside the chip or outside the chip.

A set of hexadecimal values is passed to the DAC which converts it to its corresponding analog values which is again fed to ADC which converts back to digital value. So our challenge is an array of digital values which is fed to the DAC and response is calculated from the digital values output by the ADC of the device.The microscopic variations present in the ADC and DAC components gives rise to an unique response for each device for the same set of challenges. This mixed circuit based PUF is cost effective and very efficient as it does not require expensive hardware like arbiters and oscillators for digital electronic PUFs and can be easily reproducible unlike non electronic PUFs. Moreover, ADC and DAC components are ubiquitous in modern digital devices and can be modified easily with little effort and integrated effortlessly into the current crop of devices.
